A Component-Based Sensor Network for \\ Environmental Monitoring

### 2009-03-20 docs/icccn2009/paper.tex
Kleber's feedback
git-svn-id: svn://localhost/netbeams/trunk@419 559edde2-a4d4-44e0-96fc-4035e40d7396

\author{\authorblockN{A. Puder, T. Johnson, K. Sales, M. de Sales}
\authorblockA{San Francisco State University \\
Computer Science Department \\
1600 Holloway Avenue \\
San Francisco, CA 94132 \\
EMail: \{arno$\mid$tlj$\mid$klebers$\mid$msales\}@sfsu.edu}
\and
\authorblockN{D. Robinson}
\authorblockA{San Francisco State University \\
Romberg Tiburon Center \\
3150 Paradise Drive \\
Tiburon, CA 94920 \\
EMail: dhr@sfsu.edu}}

@@

Furthermore, our work improves upon existing technologies in earlier sensor network implementations.
Many sensor networks use PIC microcontrollers \cite{Pic01} and specialized operating systems
such as TinyOS \cite{tinyos01}. However, PICs are usually too buggy,
requiring non-standard operating systems \cite{Martinez04}. Likewise, TinyOS exhibits limited 
constraints on storage, restricting any complex processing of sensor data
that can be performed \cite{Martinez04}. OSGi has been used in other sensor network
projects \cite{Mueller07, Baude07}. Although some OSGi sensor networks also include remote 
communication capabilities \cite{Rellermeyer}, our DSP is designed to support asynchronous 
communication in loosely coupled networks. It is a contribution to the OSGi
project, providing an optional way of unified loosely-coupled bundle
interaction and distributed communication. The NetBEAMS infrastructure, as
described in the paper, is available as an Open-Source project and can be 
viewed in operation at \texttt{www.netbeams.org}.

>>>>

\author{\authorblockN{A. Puder, T. Johnson, K. Sales, M. de Sales}
\authorblockA{San Francisco State University \\
Computer Science Department \\
1600 Holloway Avenue \\
San Francisco, CA 94132 \\
EMail: \{arno$\mid$tlj$\mid$kleber$\mid$msales\}@sfsu.edu}
\and
\authorblockN{D. Robinson}
\authorblockA{San Francisco State University \\
Romberg Tiburon Center \\
3150 Paradise Drive \\
Tiburon, CA 94920 \\
EMail: dhr@sfsu.edu}}

@@

Furthermore, our work improves upon existing technologies in earlier sensor network implementations.
Many sensor networks use PIC microcontrollers \cite{Pic01} and specialized operating systems
such as TinyOS \cite{tinyos01}. However, PICs are usually too buggy,
requiring non-standard operating systems \cite{Martinez04}. Likewise, TinyOS exhibits limited 
constraints on storage, restricting any complex processing of sensor data
that can be performed \cite{Martinez04}. OSGi has been used in other sensor network
projects \cite{Mueller07, Baude07}. Although some OSGi sensor networks also include remote 
communication capabilities \cite{Rellermeyer}, our DSP is designed to support asynchronous 
communication in loosely coupled networks. The NetBEAMS infrastructure, as
described in the paper, is available as an Open-Source project and can be 
viewed in operation at \texttt{www.netbeams.org}.
